Sketch Recognition and Understanding

### 2009-08-01 trunk/draft/System.tex

 \begin{equation}
\label{eq:direction}
	\vartheta  = \cos ^{ - 1} \left( {\frac{{\overrightarrow {Q_i}  \cdot \overrightarrow {O_i } }}{{\left\| {\overrightarrow {Q_i} } \right\| \times \left\| {\overrightarrow {O_i} } \right\|}}} \right)
\end{equation}
where $Q_i=\overrightarrow {P_{i - 1} P_i }$ is the vector from the point  $P_{i - 1}$ to point $P_i$ and $O_i$ represent the $x-axis$ at this point (Figure \ref{fig:curvatureCal.jpg}).  $\|{\overrightarrow {Q_i }}\|$ is the normal of the  vector $\overrightarrow{Q_i}$

@@

\subsection{Choosing the Best Fit}
\label{sec:bestFit}
The two PSO algorithms produce two segmentation solutions. After that the system evaluates each solution to finally select the best segmentation. This evaluation is based on the area of both the segmentation and the input stroke. The segmentation error($E_{alg}$ )represents the sum of Square Root Error of the length from the point on the stroke to the estimated curve or line. In \textsl{AlgS2}, this error is the same as the computed error in Equation \ref{eq:ErrorSwarm1} but For the second algorithm \textsl{AlgS2} it is different than the computed error in Equation \ref{eq:errorSwarm2}. The additional computation is necessary to  compare the two segmentation fairly. The system choose the minimum segmentaiton as the final segmentation of this stroke. 
% The segmentation which crossponds to the minimum $E_{tot}$ is the best segmentation.  
%\begin{equation}
%\label{eq:bestFit1}
%E_{area}=A_{st}-A_{sg}
% \end{equation}
% \begin{equation}
% where $A_{st}$ is the area of the input stroke, $A_{sg}$ is area of computed segmentation, $E_{alg}$ is the Segmentation Error.

@@

\section{Classification}%%Feature Set
\label{sec:Classification}
 The system uses support vector machine (SVM) classifier with Linear kernel (Linear kernel) \cite{libsvm}. SVM is a binary classifier that maximize the margin between the decision boundary and the support vectors. To enable SVM to learn multiclassifiers we used one versus one strategy for combiinig set of binary classifer. This stratgy trains $ \frac{n(n-1)}{{2}}$ binary classifier each distinguish between only two shapes. The final result is based on a number of votes each shape has from all classifiers. We used the a library implementation of LibSVM \cite{libsvm} and its implementation of the one-vs-one strategy.

>>>>

 \begin{equation}
\label{eq:direction}
	\vartheta  = \cos ^{ - 1} \left( {\frac{{\overrightarrow {Q_i}  \cdot \overrightarrow {Px_i } }}{{\left\| {\overrightarrow {Q_i} } \right\| \times \left\| {\overrightarrow {Px_i} } \right\|}}} \right)
\end{equation}
where $Q_i=\overrightarrow {P_{i - 1} P_i }$ is the vector from the point  $P_{i - 1}$ to point $P_i$ and $Px_i$ represent the $x-axis$ at this point (Figure \ref{fig:curvatureCal.jpg}).  $\|{\overrightarrow {Q_i }}\|$ is the normal of the  vector $\overrightarrow{Q_i}$

@@

\subsection{Choosing the Best Fit}
\label{sec:bestFit}
The two PSO algorithms produce two segmentation solutions. After that the system evaluates each solution to finally select the best segmentation. This evaluation is based on the area of both the segmentation and the input stroke. The segmentation error($E_{alg}$ )represents the sum of Square Root Error of the length from the point on the stroke to the estimated curve or line. In \textsl{AlgS2}, this error is the same as the computed error in Equation \ref{eq:ErrorSwarm1} but For the second algorithm \textsl{AlgS2} it is different than the computed error in Equation \ref{eq:errorSwarm2}. The additional computation is necessary to  compare the two segmentation fairly. The system choose the minimum segmentation as the final segmentation of this stroke. 
% The segmentation which crossponds to the minimum $E_{tot}$ is the best segmentation.  
%\begin{equation}
%\label{eq:bestFit1}
%E_{area}=A_{st}-A_{sg}
% \end{equation}
% \begin{equation}
% where $A_{st}$ is the area of the input stroke, $A_{sg}$ is area of computed segmentation, $E_{alg}$ is the Segmentation Error.

@@

\section{Classification}%%Feature Set
\label{sec:Classification}
The system uses support vector machine (SVM) classifier with Linear kernel (Linear kernel) \cite{libsvm}. SVM is a binary classifier that maximizes the margin between the decision boundary and the support vectors. To enable SVM to learn multi classes we used one versus one strategy for combining set of binary classifier. This strategy trains $ \frac{n(n-1)}{{2}}$ binary classifier each distinguish between only two shapes. The final result is based on a number of votes each shape has from all classifiers. We used the library implementation of LibSVM \cite{libsvm} and its implementation of the one-vs-one strategy.

\subsection{Support Vector Machines}

The foundation of Support Vector Machines (SVM) were developed by Vapnik \cite{} in 1995. It is gainig increase popularity due to the high performance and efficient implementation. The goal of SVM algorithms is to generate a sperating plane between two different classes which are represented using a set of n-dimentional vectors. The generated plane is used as a good classifier to the unseen exmaples. However, there can be more than one plane that can separates the data therefore SVM attempts to find the plane that maximize the margin (distance between classifier and nearest sample) between the two classes \ref{}. To calcuate the margin, two different hyperplanes are constructed, one plane on each side of the data, these two planes are then moved to generenate the maximum margin possilbe.

%The foundations of Support Vector Machines (SVM) have

% whate is support vector machines 
The classification problem can be restricted to consideration of the two-class problem
without loss of generality. In this problem the goal is to separate the two classes by a
function which is induced from available examples. The goal is to produce a classifier
that will work well on unseen examples, i.e. it generalises well. Consider the example
in Figure 2.1. Here there are many possible linear classifiers that can separate the data,
but there is only one that maximises the margin (maximises the distance between it
and the nearest data point of each class). This linear classifier is termed the optimal
separating hyperplane. Intuitively, we would expect this boundary to generalise well as
opposed to the other possible boundaries.

%The above is a classic example of a linear classifier, i.e., a classifier that separates a set of objects into their respective groups (GREEN and RED in this case) with a line. Most classification tasks, however, are not that simple, and often more complex structures are needed in order to make an optimal separation, i.e., correctly classify new objects (test cases) on the basis of the examples that are available (train cases). This situation is depicted in the illustration below. Compared to the previous schematic, it is clear that a full separation of the GREEN and RED objects would require a curve (which is more complex than a line). Classification tasks based on drawing separating lines to distinguish between objects of different class memberships are known as hyperplane classifiers. Support Vector Machines are particularly suited to handle such tasks.

% how decisions is made
%  how training is done 
% how testing is donel. 
% kernels 
% how multi classifier are implemented 
% how parameter for cost is measured. 
% advantages 
% disadavantages 
% importance and applications used in it.
